Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-01 ms.tex
conclusions1

\begin{figure}
\includegraphics[width=\columnwidth]{mdot_sfr.pdf}
\caption{\label{fig:bh_growth} {\it Top panel:} Critical values of the
  black hole accretion rate $\dot{M}$ in Eddington units as a function
  of black hole mass $M_{\bullet}$, shown separately for core
  ($\Gamma=0.1$, solid lines) and cusp galaxies ($\Gamma=0.8$,
  dot-dashed lines).  Black lines show the accretion rate calculated
  from equation (\ref{eq:eddr_analytic}) using our estimate of the gas
  heating rate provided at $z = 0$ by the average star formation
  histories for each galaxy mass (Fig.~\ref{fig:vwSources}).  Green
  lines show the maximum accretion set by Ia supernovae blow-out
  (\ref{eq:eddr_Ia}).  Red lines show the accretion rate so obtained
  if Compton heating alone was acting (eq.~[\ref{eq:MdotC}]).  Yellow
  lines show the maximum accretion rate for a thermally stable flow
  near the stagnation radius (eq.~[\ref{eq:Mdotmax}]).  We also show
  Eddington ratios inferred for SgrA* from
  \citet{Quataert:2004a} (line with black circle), for NGC3115 from
  \citet{ShcherbakovWong+:2014a} (line with black diamonds), and for
  the Swift J1644+57 TDE from \citet{BergerZauderer+:2012a} (line
  with black crosses) {\it Bottom panel:} Growth times $\Mbh/\Mdot$
  in units of the Hubble time $\th$ for each of the accretion rates
  shown in the top panel.}
\end{figure}

@@

We have calculated steady-state models for circumnuclear medium of
quiescent galaxies, assuming that gas is supplied entirely by stellar
wind mass loss and heated by shocked stellar winds, supernovae and
black hole feedback. We compute profiles for a range of different
black hole masses, heating rates, and stellar density profiles and use
these profiles to calculate an $\Mdot$ onto each galaxy's SMBH, and
get the scaling of $\Mdot$ with $\Mbh$. We may then compare our
results with observed trends of nuclear x-ray luminosity with galaxy
properties. Our main conclusions may be summarized as follows.

  \begin{enumerate}
  %Younger population=>higher accretion rate; generally higher eta and
  %lower vw except for very young stellar populations.
  \item The gas will be divided between an accretion flow and an
    outward flow at the stagnation radius, $\rs$. In a steady state
    the gas inflow rate towards the hole will be proportional to the
    stellar mass enclosed inside of $\rs$. 
  \item The location of the stagnation radius and thus the accretion
    rate is quite sensitive to the effective heating rate of the
    gas. In our model gas is supplied by stellar winds and the kinetic
    energy of the winds is thermalized as the winds
    collide. Supernovae and AGN feedback may provide additional
    sources of heating. Each source of heating is related to the star
    formation history of the galaxy.  For example, a galaxy with star
    formation within the last $\sim10^7$ years would have mass
    injection from very fast stellar winds ($w_w\simeq 1000$ km/s). In
    contrast, an older population would have heating only from AGN
    feedback and supernovae.

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{mdot_sfr.pdf}
\caption{\label{fig:bh_growth} {\it Top panel:} Critical values of the
  black hole accretion rate $\dot{M}$ in Eddington units as a function
  of black hole mass $M_{\bullet}$, shown separately for core
  ($\Gamma=0.1$, solid lines) and cusp galaxies ($\Gamma=0.8$,
  dot-dashed lines).  Black lines show the accretion rate calculated
  from equation (\ref{eq:eddr_analytic}) using our estimate of the gas
  heating rate provided at $z = 0$ by the average star formation
  histories for each galaxy mass (Fig.~\ref{fig:vwSources}).  Green
  lines show the maximum accretion set by Ia supernovae blow-out
  (\ref{eq:eddr_Ia}).  Red lines show the accretion rate so obtained
  if Compton heating alone was acting (eq.~[\ref{eq:MdotC}]).  Yellow
  lines show the maximum accretion rate for a thermally stable flow
  near the stagnation radius (eq.~[\ref{eq:Mdotmax}]).  We also show
  Eddington ratios inferred for SgrA* from
  \citet{Quataert:2004a} (black circles), for NGC3115 from
  \citet{ShcherbakovWong+:2014a} (black diamonds), and for
  the Swift J1644+57 TDE from \citet{BergerZauderer+:2012a} (black crosses) {\it Bottom panel:} Growth times $\Mbh/\Mdot$
  in units of the Hubble time $\th$ for each of the accretion rates
  shown in the top panel.}
\end{figure}

@@

We have calculated steady-state models for the hot gaseous circumnuclear media of quiescent galaxies, under the assumption that gas is supplied exclusively by stellar wind mass loss and heated by shocked stellar winds, supernovae and black hole feedback.  We compute solutions for a range of different black hole masses, heating rates, and stellar density profiles.  Our numerical results (Table \ref{table:models}) are used to verify and calibrate analytic relationships (Appendix \ref{app:rs}, \ref{app:be}), which are in turn used to calculate the black hole accretion rate and how it varies with $\Mbh$ and the galaxy's star formation history.  Our results for $\dot{M}(\Mbh)$ are compared with observed trends of the nuclear X-ray luminosities of quiescent SMBHs and low luminosity AGN, as well as to address other key questions, such as the thermal stability of their accretion flows.  Our conclusions may be summarized as follows.

  \begin{enumerate}
  %Younger population=>higher accretion rate; generally higher eta and
  %lower vw except for very young stellar populations.
  \item The stagnation radius, $\rs$, divides the nuclear gas between an accretion flow and an
    outward wind. In a steady state the gas inflow rate towards the black hole will be proportional to the
    stellar mass enclosed inside of $\rs$. 
  \item The location of the stagnation radius and thus the accretion
    rate is very sensitive to the effective heating rate of the
    gas.  Stellar wind heating, supernovae, and AGN feedback depend on the black hole mass as well as the star
    formation history of the galaxy.  For example, for a galaxy with star formation within the last $\sim10^7$ years, both mass and energy injection are dominated by fast stellar winds from young stars ($w_w\simeq 1000$ km/s). In contrast, a galaxy with star formation relegated to the distant pass would have mass input dominated by old stars and heating dominated by AGN feedback and supernovae.  The energy input for galaxies with ongoing, continuous star formation is usually dominated by the youngest stars, while mass input is dominated by the old stellar poupation.
